Unsupervised learning of Gaussian mixture models in linear time using a variational Bayesian method

### 2017-05-17 articles/nips-2017/ms.tex
bah

\section{Introduction}
% Gaussian mixture modelling is a common problem.
% When the number of mixtures is unknown, the problem is normally 
% attacked by optimizing multiple different models, and performing
% model selection after-the-fact.
% Model selection is typically governed by a penalized heuristic,
% e.g., BIC, AIC, etc.

@@

\noindent{}where $\vecmean$ and $\veccov$ is the multivariate mean and 
covariance matrix, and $\data$ are the data.
For a fixed number of $K$ multivariate Gaussian mixtures, the probability
density function is given by:

@@

The mixing weights follow a multinomial distribution.  For this reason,
although the weights of future mixtures are not known, it can be shown that
the sum of the log of $K$ weights follow the function,
\begin{equation}
  \sum_{k=1}^{K+\Delta{K}}\log\weight_k\future \approx -K\log{K} + g_0
  \label{eq:g}
\end{equation}

@@

% Initialization

@@

%

@@

\section{Conclusion}

>>>>

\section{Introduction}
\label{sec:introduction}

% Gaussian mixture modelling is a common problem.
% When the number of mixtures is unknown, the problem is normally 
% attacked by optimizing multiple different models, and performing
% model selection after-the-fact.
% Model selection is typically governed by a penalized heuristic,
% e.g., BIC, AIC, etc.

@@

\noindent{}where $\vecmean$ and $\veccov$ is the multivariate mean and 
covariance matrix, and the data $\data$ is an $N\times{}D$ array.
For a fixed number of $K$ multivariate Gaussian mixtures, the probability
density function is given by:

@@

The mixing weights follow a multinomial distribution.  For this reason,
although the weights of future mixtures are not known, it can be shown that
the sum of the log of $K$ weights follow the function,
\begin{equation}
  \sum_{k=1}^{K+\Delta{K}}\log\weight_k\future \leq -K\log{K} + g_0
  \label{eq:g}
\end{equation}

@@

\subsection{Initialization}

\subsection{Mixture optimization}

Every time a mixture is perturbed and optimized, we store the
resulting mixture predictors $\{K, \sum_{k=1}^{K}\log\weight_k, X\}$ in order
to update our approximating functions $G(K)$ and $H(K)$.

\subsection{Perturbation search}

Starting from our initial mixture, we adopt a perturbation search strategy 
which considers the following possible perturbations: merge, delete, split,
and jump.  We briefly describe each step in turn.

% DESCRIBE EACH ONE.

While perturbation search strategies have existed for Gaussian
mixture models for some time, none have included a \emph{jump} operation.
With our approximating functions to calculate probability densities for the
message length of future mixtures, including a \emph{jump} operation allows
us to quickly move to the appropriate number of mixture components.

@@

% The K=4 mixture in F & J 2002, etc.

@@

% A huge model.

% Cost of the model.

\section{Discussion}
